### 2020-01-24 thesis_template/2_RelatedWork/relatedWork.tex

>>>>

\section{Elements Copy and Insertion into Size-initialized Vector in Rust}
\label{sec:history}
In this experiment, three methods to insert elements into vector in Rust. One is clone method which is performs bitwise deep copy.
Another is copy_nonoverlapping function which copies values from source to distination memory region. 
The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted, 1000, 10000, 100000, 1000000 and, 
their runtime for each
